Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-19 paper/paper.tex
pass on mining

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\filesAttached{} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\filesMining{} files. All those files were included in
Table~\ref{tab:test-suites}. For the classification of ``code''
vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
NLP technique to produce word embeddings. A word embedding is a
mapping of words---in our case, sentences---to vectors of real
numbers. With that mapping it is possible to measure distance between
two sentences as the distance between the vectors characterizing
them. Consequently, one can measure, for example, the minimum distance
between a sentence in English and a sentence in a \js\ embedding,
built with word2vec using a corpus of \js\ sentences. \Mar{Please
  confirm if this is the idea! If yes, shouldn't just one corpus
  (e.g., the JS corpus) be enough to solve the problem? Are there two
  separate embeddings (one for English and one for JS)? If not, how
  they are combined? What about the classification scheme?  It needs
  to answer yes/no (not a distance).}  We used a corpus with \samplesEnglish{}
samples of English paragraphs and \samplesJSSnippets{} snippets of \js{} code and
obtained a classifier with accuracy of \accuracyMining{}. This classifier is
publicly available from our website as a separate component.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.  (We omitted the URLs of the issues to protect anonymity.)
Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
and \smonkey{}~\cite{mozilla-severity} developers use five levels,
whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} developers use only three. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') in place of the severity level for the cases where
the bug report is pending confirmation. Of the
\noBugsTransplantation{} bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
not find any critical bugs, most of the bugs are seemingly important
as per the categorization given by engineers. Analyzing the issue
tracker of \chakra, we found that severity-1 bugs are indeed
rare. Considering the number of bug reports confirmed by developers,
\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
fixed). Considering the remaining engines, \veight{} developers
confirmed the \bugsVeight{} bugs we reported, fixing \bugsVeightFixed{}. Curiously, Google
engineers confirmed the issued bug reports in a few hours. Overall, we
found that development teams of other engines, specially \jsc\, took
much longer to analyze bug reports as can be observed in the
\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
However, the bugs the \jsc{} team confirmed were quickly fixed.

>>>>

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\filesAttached{} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\filesMining{} files. All those files were included in
Table~\ref{tab:test-suites}. For the classification of ``code''
vs. ``not code'',

% we used word2vec~\cite{kusner2015word}, a popular
% NLP technique to produce word embeddings. A word embedding is a
% mapping of words---in our case, sentences---to vectors of real
% numbers. With that mapping it is possible to measure distance between
% two sentences as the distance between the vectors characterizing
% them. Consequently, one can measure, for example, the minimum distance
% between a sentence in English and a sentence in a \js\ embedding,
%   built with word2vec using a corpus of \js\ sentences.
% \Mar{Please
%   confirm if this is the idea! If yes, shouldn't just one corpus
%   (e.g., the JS corpus) be enough to solve the problem? Are there two
%   separate embeddings (one for English and one for JS)? If not, how
%   they are combined? What about the classification scheme?  It needs
%   to answer yes/no (not a distance).}
% We used a corpus with \samplesEnglish{}
% samples of English paragraphs and \samplesJSSnippets{} snippets of \js{} code and
% obtained a classifier with accuracy of \accuracyMining{}. This classifier is
% publicly available from our website as a separate component.

\Igor{
  we used a corpus with \samplesEnglish{} samples of English 
  paragraphs and \samplesJSSnippets{} snippets of \js{} code.
  To process the corpus we used word2vec~\cite{kusner2015word}, a popular
  NLP technique to produce word embeddings as an input for a Multi-Layer Perceptron (MLP).
  A word embedding is a mapping of tokens that represents 
  words---in our case, sentences---to vectors of real
  numbers. The output of word2vec gives the context and extra informations about the tokens,
  for example the distance between them. Consequently, one can measure, for example, the minimum distance
  between a token in English and a token in a \js\ embedding, using a corpus of \js\ sentences.
  We used a simple supervised MLP to train and predicted the inputs, 
  the classifier obtained accuracy of \accuracyMining{}. This classifier is
  publicly available from our website as a separate component.
}

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.  (We omitted the URLs of the issues to protect anonymity.)
Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
and \smonkey{}~\cite{mozilla-severity} developers use five levels,
whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} developers use only three. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') in place of the severity level for the cases where
the bug report is pending confirmation. Of the
\noBugsTransplantation{} bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
not find any critical bugs, most of the bugs are seemingly important
as per the categorization given by engineers. Analyzing the issue
tracker of \chakra, we found that severity-1 bugs are indeed
rare. Considering the number of bug reports confirmed by developers,
\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
fixed). Considering the remaining engines, \veight{} developers
confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
\noTransVeightBugsFixed{}. Curiously, Google
engineers confirmed the issued bug reports in a few hours. Overall, we
found that development teams of other engines, specially \jsc\, took
much longer to analyze bug reports as can be observed in the
\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
However, the bugs the \jsc{} team confirmed were quickly fixed.
